Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-06-05 paper/main.tex
final version finished?

Figure~\ref{fig:quantile} presents the time spent by multi-level
reduction on individual automata of each automata set. The chart
shows a pleasing finding that for every set, most automata are reduced
in under a second and the high cumulative running times are caused by 
a relatively small number of complicated automata.

\ref{fig:quantile-random}

\begin{figure}[t]
  \caption{Performance of \telatko on individual automata of each automata sets.
    The graph shows the time ($y$ axis) needed by \telatko
    to process the $x$-th automaton of the set, where automata of each set are ordered by their processing time.
    % The $x$ axis represents the number of automata from each automata
    % set that are processed by \telatko in the time shown on the $y$
    % axis.
  }
\label{fig:quantile}
\bigskip
\centering
\input{quantile.tex}
\end{figure}

\begin{figure}[t]
  \caption{Quantile random.}
\label{fig:quantile-random}
\bigskip
\centering
\input{quantile-random.tex}
\end{figure}

@@

We have presented a method reducing the number of acceptance marks in
transition-based Emerson-Lei automata with use of QBF solving and
without altering automata structure. We have implemented the method in
a tool called \texttt{telatko}. The current applications of the tool
are twofold. First, it can reduce the number of acceptance marks of a
given TELA. Second, it discloses how tools producing TELA are
economical with acceptance marks. The presented experimental results
show that the tool can indeed reduce the number of acceptance marks in
automata produced by all considered state-of-the-art LTL to automata
translators on formulas from literature. Further, it clearly shows
that the translators of the Owl library are significantly less
economical with acceptance marks than the other two translators.

@@

In the future, we plan to improve the reduction process (e.g., use the
bisection method to reduce the number of acceptance marks more
efficiently) and study whether the reduction of acceptance condition
can enable further reductions or simplifications of automata
structures.

>>>>

\begin{figure}[p]
  \centering
  \input{quantile.tex}
  \bigskip\bigskip
  \input{quantile-random.tex}
  \bigskip
  \caption{Performance of \telatko on individual automata of each automata set.
    Automata sets constructed from formulas from literature are in the upper graph,
    automata sets constructed from random formulas are in the lower graph.
    Each line shows the time ($y$ axis) needed by \telatko to process the
    $x$-th automaton of the set, where automata in the set are ordered by
    their processing time.
    % The $x$ axis represents the number of automata from each automata
    % set that are processed by \telatko in the time shown on the $y$
    % axis.
  }
\label{fig:quantile}\end{figure}

Figure~\ref{fig:quantile} presents the time spent by multi-level
reduction on individual automata of each automata set. The charts
show a pleasing finding that for every set, most automata are reduced
in under 5 seconds and the high cumulative running times are caused by 
a relatively small number of complicated automata.

@@

We have presented a method reducing the number of acceptance marks in
transition-based Emerson-Lei automata with use of QBF solving and
without altering automata structure. We have implemented the method in
a tool called \texttt{telatko}. The current applications of the tool
are twofold. First, it can reduce the number of acceptance marks of a
given TELA. Second, it discloses how tools producing TELA are
economical with acceptance marks. The presented experimental results
show that the tool can indeed reduce the number of acceptance marks in
automata produced by all considered state-of-the-art LTL to automata
translators. Further, it clearly shows that the translators of the Owl
library are significantly less economical with acceptance marks than
the other two translators.

@@

% In the future, we plan to improve the reduction process (e.g., use the
% bisection method to reduce the number of acceptance marks more
% efficiently) and study whether the reduction of acceptance condition
% can enable further reductions or simplifications of automata
% structures.
